An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-03 tex/paper.tex
Adding Moran processes to what the library can do.
Removing self references.

This paper introduces a software package: the Axelrod-Python library
\cite{Axelrod-Pythonprojectteam2015}. The Axelrod-Python project has the
following stated goals:

@@

Further to these evolutionary ideas, \cite{Chellapilla1999, DavidB1993} are
examples of using machine learning techniques to evolve particular strategies.
In \cite{Axelrod}, Axelrod describes how similar techniques are used to
genetically evolve a high performing strategy from a given set of strategies.
Note that in his original work, Axelrod only used a base strategy set of 12
strategies for this evolutionary study. This is noteworthy as
\cite{Axelrod-Pythonprojectteam2015} now boasts over 135 strategies that are
readily available for a similar analysis.

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{number_of_strategies_with_arima_projection.pdf}
	\caption{The number of strategies included in the library}
	\label{fig:number_of_strategies_against_date}
\end{figure}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Noisy tournaments.
    \item Tournaments with probabilistic ending of interactions.
    \item Ecological analysis of tournaments.
    \item Morality metrics based on \cite{Singer-Clark2014}.
    \item Transformation of strategies (in effect giving an infinite number of
        strategies).
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
    \item Parallelization of computations for tournaments with a high
        computational cost \cite{Pathos, Mckerns2011}.
\end{itemize}

>>>>

This paper introduces a software package: the Axelrod-Python library. The
Axelrod-Python project has the following stated goals:

@@

Further to these evolutionary ideas, \cite{Chellapilla1999, DavidB1993} are
examples of using machine learning techniques to evolve particular strategies.
In \cite{Axelrod}, Axelrod describes how similar techniques are used to
genetically evolve a high performing strategy from a given set of strategies.
Note that in his original work, Axelrod only used a base strategy set of 12
strategies for this evolutionary study. This is noteworthy as
the library now boasts over 135 strategies that are
readily available for a similar analysis.

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{number_of_strategies.pdf}
	\caption{The number of strategies included in the library}
	\label{fig:number_of_strategies_against_date}
\end{figure}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Noisy tournaments.
    \item Tournaments with probabilistic ending of interactions.
    \item Ecological analysis of tournaments.
    \item Moran processes.
    \item Morality metrics based on \cite{Singer-Clark2014}.
    \item Transformation of strategies (in effect giving an infinite number of
        strategies).
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
    \item Parallelization of computations for tournaments with a high
        computational cost \cite{Pathos, Mckerns2011}.
\end{itemize}
